### 2024-10-26 paper/3-motivation.tex
Minor change

It might be easy to understand how the \officialp{} explains the control flow
of WebAssembly, if we assume that a WebAssembly code is loaded on a memory and
a pc points to the instruction to execute.
To describe control flow, it uses a structure named \textit{block} which
consitutes of a instruction sequence.
When executing the instruction sequence inside the block, it can jump to the
starting point of the block or the end of the block.

@@

Example 1 is a WebAssembly code example that has a \texttt{loop} whose result
type is \texttt{i32} and has a block of three instructions: \texttt{i32.const},
\texttt{br}, \texttt{unreachable}.
\cref{loop-fig} is the \officialp{} of \texttt{loop} instruction.
It says that the continuation is the start of the loop, the information is
stored in a label, and it \textit{enters} the block with the label.
The term enter means that it pushes the label in the stack and makes pc points
to the first instruction in the block.
\texttt{i32.const} instruction is executed first, which just pushes the
value in the stack.
Then, \texttt{br} instruction is executed.
\cref{br-fig} is the \officialp{} of \texttt{br} instruction.
It pops the label from the stack, and makes pc points to the continuation of
the label, which is the start of the loop instruction.
As a result, the code example above is a infinite loop pushing a \texttt{i32}
value \texttt{42} infinitely.

>>>>

It might be easy to understand how the \officialp{} explains the control flow
of WebAssembly, if we assume that a WebAssembly code is loaded on a memory and
a pc points to the instruction to execute.
To describe control flow, it uses a structure named \textit{block} which
consitutes of a instruction sequence.
When executing the instructions in the block, pc can be changed to the starting
point of the block or the end of the block.

@@

Example 1 is a WebAssembly code example that has a \texttt{loop} whose result
type is \texttt{i32} and has a block of three instructions: \texttt{i32.const},
\texttt{br}, \texttt{unreachable}.
\cref{loop-fig} is the \officialp{} of \texttt{loop} instruction.
It says that the continuation is the start of the loop, the information is
stored in a label, and it \textit{enters} the block with the label.
The term \textit{enter} means that it pushes the label in the stack and makes
pc points to the first instruction in the block.
\texttt{i32.const} instruction is executed first, which just pushes the
\texttt{i32} value \texttt{42} in the stack.
Then, \texttt{br} instruction is executed.
\cref{br-fig} is the \officialp{} of \texttt{br} instruction.
It pops the label from the stack, and makes pc points to the continuation of
the label, which is the start of the loop instruction.
As a result, the code example above is a infinite loop pushing \texttt{42}
forever.
